---
title: "ThreeME Standard results"
author: "ThreeME team"
date: "`r format(Sys.Date(), '%d %B %y')`"
format: 
 revealjs:
  center: true
  navigation-mode: linear
  theme: [simple, results/report/markdown/src/presentation.scss]
  width: 1200
  height: 700
  subtitle: 'Scenario: `params$scenario_to_analyse`'
params:
  startyear: 2020
  endyear: 2030
  project_name: "multi_shock"
  project_title: "Simulation with small general equilibrium model"
  scenario_to_analyse: ct1
  classification: "c4_s4"
  template_default: ofce
number-sections: true
---


```{r setup, include=FALSE}

work.dir <- stringr::str_remove(getwd(),"/results/report/markdown")
knitr::opts_knit$set(root.dir = work.dir)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide"
)
```


```{r Plots default options}

startyear <- params$startyear
endyear <- params$endyear
scenario_to_analyse <- params$scenario_to_analyse
classification <- params$classification
template_default <- params$template_default
project_name <- params$project_name

scenario <- scenario_to_analyse
scenario_name <- scenario_to_analyse
```


```{r Required packages, message=FALSE, warning=FALSE}
# Load functions
source("src/functions.R")

```




```{r Create database function, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# Create the database for further processing
#source("src/0_create_databases.R")

```

```{r load data and bridges}

data_full<-readRDS(file = file.path("data","output", paste0(project_name,".rds")))

### BUG : mettre le bon: pb avec secteurs
data_com_sec<-readRDS(file = file.path("data","output", paste0(project_name,".rds")))


# data_full<-readRDS(file = paste0("data/output/",scenario_to_analyse,"_",classification,".rds"))
# ### loading the sector and commodity aggregated database 
# data_com_sec <- readRDS(file =paste0("data/output/",scenario_to_analyse,"_",classification,".rds"))

source(paste0("src/bridges/bridge_",classification,".R"))
source(paste0("src/bridges/codenames_",classification,".R"))

```

# Macroeconomic results

## Result summary

```{r results ='asis'}
#| label: tbl-macro
#| tbl-cap: Macro Res
#| eval: false 

table <- table.output(data = data_com_sec, scenario = scenario_to_analyse, 
             full.table = TRUE, export.doc = FALSE, langue = "en",
             title = 'Macroeconomic main results')

table

```

## GDP and its components

```{r Graph GDP,  fig.height = 6, fig.width = 14}

variables_selection = c("M","X", "CH", "I", "G","DS", "GDP")
label_macro <- c("Gross domestic product", "Households consumption", "Investment", "Public spending")
A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, titleplot = "GDP and its components  (in difference from baseline)")

B <- simpleplot(data_full,c("X", "M", "BAL_TRADE"),label_series = c("Exports", "Imports", "Trade balance"), startyear, endyear, titleplot = "External trade  (in difference from baseline)")

ggarrange(A,B,
        labels = c("(a)", "(b)"),
        hjust = -0.5, vjust = 1.5,
        ncol = 2, nrow = 1,
        widths = 2,  heights = 1)

```

## GDP and its components (Growth rate)

```{r Graph Macro Growth rate, fig.height = 6, fig.width=14}

A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, "gr", titleplot = "GDP and its components (growth rates)")

B <- simpleplot(data_full,c("X", "M"), c("Exports", "Imports"), startyear, endyear, "gr", titleplot = "External trade (growth rates)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Contribution to the GDP change relative to the baseline (expenditure approach)

```{r contrib GDP expenduture, fig.height=6, fig.width=14}

variables_selection = c("M","X", "CH", "I", "G","DS", "GDP")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          BAL_TRADE = X - M,
          CH_G = CH + G,
          I_DS = I + DS)
      
      ) %>% 
  long_data()

contrib_comp <- c( "CH_G", "I_DS", "BAL_TRADE")
contrib_comp_label <- c( "Final consumption", "Investment", "Trade balance")

data_plot <-  contrib(new_indicators,"GDP", contrib_comp, scenar = c("baseline",scenario_name))

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in GDP (in difference from baseline)", line_tot = TRUE)

contrib_comp <- c( "X", "M")
contrib_comp_label <- c("Exports", "Imports")

data_plot <-  contrib(new_indicators,"BAL_TRADE", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "M")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in trade balance (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Contribution to the GDP change relative to the baseline (income approch)

```{r contrib GDP income, fig.height=6, fig.width=14}

contrib_comp <- c( "VA", "NTAXC")
contrib_comp_label <- c( "Value-Added","Net taxes on products")

data_plot <-  contrib(data_full,"GDP", contrib_comp, scenar = c("baseline",scenario_name))

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in GDP (in difference from baseline)", line_tot = TRUE)

contrib_comp <- c("GOS", "WAGES", "RSC", "NTAXS")
contrib_comp_label <- c("Gross operating surplus", "Gross wages", "Employers social contributions", "Net taxes on the production")

data_plot <-  contrib(data_full,"VA", contrib_comp, scenar = c("baseline",scenario_name))

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
              startyear = startyear, endyear = endyear, titleplot = "Contributions to change in value-added (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Value-added and its components

```{r Prod_VA, fig.height = 6, fig.width=14}

contrib_comp <- c("Y", "CI")
contrib_comp_label <- c("Production", "Intermediary consumption")

A <- simpleplot(data_full,c(contrib_comp, c("VA")), c(contrib_comp_label,c("Value-added")), startyear, endyear, titleplot = "Value-added and its components (in difference from baseline)")

data_plot <-  contrib(data_full,"VA", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "CI")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to changes in Value-Added (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Employment

```{r Employment, fig.height = 6, fig.width=14}

A <- simpleplot(data_full,"F_L", label_series = "Labor", startyear, endyear, decimal = 1, titleplot = "Employment (in difference from baseline)")
B <- simpleplot(data_full,"F_L", label_series = "Labor", startyear, endyear, "diff", unit = 1000, decimal = 1, titleplot = "Employment (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Unemployment

```{r Unemployment, fig.height = 6, fig.width=14}

C <- simpleplot(data_full,"UNR", label_series = "Unemployment", startyear, endyear,"diff", unit = 100, titleplot = "Unemployment rate (in difference from baseline)")
D <- simpleplot(data_full,"UNR", label_series = "Unemployment rate (dashed line = baseline)", startyear, endyear, "level", titleplot = "Unemployment rate  (level)")

ggarrange(C,D,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

# Government


## Debt of the Government

```{r Gov_Debt, fig.height = 6, fig.width=14}

variable_macro <- c("RDEBT_G_VAL") %>% toupper()
label_macro <- c("Debt")

A <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"diff", unit = 100, titleplot = "Debt to GDP ratio (in difference from baseline)")

B <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"level", unit = 100, titleplot = "Debt to GDP ratio (dashed line = baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Savings/deficit of the Government

```{r Gov_Savings_deficit, fig.height = 6, fig.width=14}

variable_macro <- c("RSAV_G_VAL", "RBal_G_Prim_VAL", "RBal_G_Tot_VAL") %>% toupper()
label_macro <- c("Savings", "Primary balance", "Total balance")

A <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"diff", unit = 100, titleplot = "Saving to GDP ratio indicators (in difference from baseline)")

B <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"level", unit = 100, titleplot = "Saving to GDP ratio indicators  (dashed line = baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

The **Savings of the Government** corresponds to the net lending/borrowing (Income minus spending), which is the published deficit/savings of the Government.

The **Total balance of the Government** corresponds to the savings excluding the reimbursement of the debt from the Government spending. 

The **Primary balance of the Government** corresponds to the savings excluding the reimbursement and the interest paid on the debt from the Government spending. 


## Incomes and spending of the Government

```{r Gov_Savings_Inc_spend, fig.height = 6, fig.width=14}

A <- simpleplot(data_full, c("INC_G_VAL", "SPEND_G_VAL"), label_series =  c("Incomes", "Spending"), startyear, endyear, transformation = "reldiff", titleplot = "Incomes and spending  (in difference from baseline)")

A 

# contrib_comp <- c( "INC_G_VAL", "SPEND_G_VAL")
# contrib_comp_label <- c("Incomes", "Spending")
# 
# data_plot <-  contrib(data_full,"SAV_G_VAL", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "SPEND_G_VAL")
# 
# B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
#              startyear = startyear, titleplot = "Contributions to change in Saving (in difference from baseline)", line_tot = TRUE)
# 
# 
# ggarrange(A,B,
# labels = c("(a)", "(b)"),
# hjust = -0.5, vjust = 1.5,
# ncol = 2, nrow = 1,
# widths = 2,  heights = 1)


```

## Carbon tax incomes (as a percentage of GDP)

```{r Gov_Carbon Tax, fig.height=6, fig.width=14}

variables_selection = c("T2VAL_SEC","T2VAL_CH", "GDP")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          R_T2VAL_SEC_GDP = T2VAL_SEC / GDP,
          R_T2VAL_CH_GDP = T2VAL_CH / GDP,
          R_T2VAL_GDP = (T2VAL_SEC + T2VAL_CH) / GDP
          )

      ) %>% 
  long_data()

contrib_comp <- c( "R_T2VAL_SEC_GDP", "R_T2VAL_CH_GDP")
contrib_comp_label <- c("Sectors", "Households")

A <- simpleplot(new_indicators, series = contrib_comp, label_series = contrib_comp_label, startyear, endyear, "level", titleplot = "Carbon tax incomes per agent (dashed line = baseline)")


if (new_indicators$baseline[which(new_indicators$year == startyear & new_indicators$variable=="R_T2VAL_GDP")]==0) {
B <- simpleplot(new_indicators, series = "R_T2VAL_GDP", label_series = contrib_comp_label, startyear, endyear, "level", titleplot = "Total carbon tax incomes (dashed line = baseline)")

} else {
  data_plot <-  contrib(new_indicators,"R_T2VAL_GDP", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
              startyear = startyear, titleplot = "Contributions to the change in Carbon tax incomes (in difference from baseline)", line_tot = TRUE)

}


ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

```

## Prices and wages 

```{r Graph Prices, fig.height = 6, fig.width=14}
label_prices <- c("Consumption", "Production", "Value added","Imports", "Exports")
A <- simpleplot(data_full,c("PCH", "PY", "PVA", "PM", "PX"),label_prices, startyear, endyear, titleplot = "Prices (in difference from baseline)")
B <- simpleplot(data_full,"W", label_series = "wage", startyear, endyear, titleplot = "Gross nominal wages (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust =-0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```
