---
title: "ThreeME Standard results"
author: "ThreeME team"
date: "`r format(Sys.Date(), '%d %B %y')`"
format: revealjs
subtitle: 'Scenario: `r params$scenario_to_analyse`'
params:
  startyear: 2020
  endyear: 2030
  project_name: "multi_shock"
  project_title: "Simulation with small general equilibrium model"
  scenario_to_analyse: ct1
  classification: c4_s4
  template_default: ofce
number-sections: true
---


```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide"
)

```


```{r}
#| label: Plots default options


startyear <- params$startyear
endyear <- params$endyear
scenario_to_analyse <- params$scenario_to_analyse
classification <- params$classification
template_default <- params$template_default
project_name <- params$project_name

scenario <- scenario_to_analyse
scenario_name <- scenario_to_analyse
```


```{r}
#| label: Required packages
#| message: false
#| warning: false

# Load functions
source("src/functions.R")

```




```{r}
#| label: Create database function
#| include: false
#| eval: false
#| message: false
#| echo: false

# Create the database for further processing
#source("src/0_create_databases.R")

```

```{r}
#| label: load data and bridges


data_full<-readRDS(file = file.path("data","output", paste0(project_name,".rds")))

### BUG : mettre le bon: pb avec secteurs
data_com_sec<-readRDS(file = file.path("data","output", paste0(project_name,".rds")))


# data_full<-readRDS(file = paste0("data/output/",scenario_to_analyse,"_",classification,".rds"))
# ### loading the sector and commodity aggregated database 
# data_com_sec <- readRDS(file =paste0("data/output/",scenario_to_analyse,"_",classification,".rds"))

source(paste0("src/bridges/bridge_",classification,".R"))
source(paste0("src/bridges/codenames_",classification,".R"))

```

# Macroeconomic results

## Result summary

```{r}
#| label: tbl-macro
#| tbl-cap: Macro Res

table <- table.output(data = data_com_sec, scenario = scenario_to_analyse, 
             full.table = TRUE, export.doc = FALSE, langue = "en",
             title = 'Macroeconomic main results')

table

```

## GDP and its components

```{r}
#| label: Graph GDP
#| fig-height: 6
#| fig-width: 14

variables_selection = c("M","X", "CH", "I", "G","DS", "GDP")
label_macro <- c("Gross domestic product", "Households consumption", "Investment", "Public spending")
A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, titleplot = "GDP and its components  (in difference from baseline)")

B <- simpleplot(data_full,c("X", "M", "BAL_TRADE"),label_series = c("Exports", "Imports", "Trade balance"), startyear, endyear, titleplot = "External trade  (in difference from baseline)")

ggarrange(A,B,
        labels = c("(a)", "(b)"),
        hjust = -0.5, vjust = 1.5,
        ncol = 2, nrow = 1,
        widths = 2,  heights = 1)

```

## GDP and its components (Growth rate)

```{r Graph Macro Growth rate, fig.height = 6, fig.width=14}

A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, "gr", titleplot = "GDP and its components (growth rates)")

B <- simpleplot(data_full,c("X", "M"), c("Exports", "Imports"), startyear, endyear, "gr", titleplot = "External trade (growth rates)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Contribution to the GDP change relative to the baseline (expenditure approach)

```{r contrib GDP expenduture, fig.height=6, fig.width=14}

variables_selection = c("M","X", "CH", "I", "G","DS", "GDP")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          BAL_TRADE = X - M,
          CH_G = CH + G,
          I_DS = I + DS)
      
      ) %>% 
  long_data()

contrib_comp <- c( "CH_G", "I_DS", "BAL_TRADE")
contrib_comp_label <- c( "Final consumption", "Investment", "Trade balance")

data_plot <-  contrib(new_indicators,"GDP", contrib_comp, scenar = c("baseline",scenario_name))

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in GDP (in difference from baseline)", line_tot = TRUE)

contrib_comp <- c( "X", "M")
contrib_comp_label <- c("Exports", "Imports")

data_plot <-  contrib(new_indicators,"BAL_TRADE", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "M")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in trade balance (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Contribution to the GDP change relative to the baseline (income approch)

```{r contrib GDP income, fig.height=6, fig.width=14}

contrib_comp <- c( "VA", "NTAXC")
contrib_comp_label <- c( "Value-Added","Net taxes on products")

data_plot <-  contrib(data_full,"GDP", contrib_comp, scenar = c("baseline",scenario_name))

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in GDP (in difference from baseline)", line_tot = TRUE)

contrib_comp <- c("GOS", "WAGES", "RSC", "NTAXS")
contrib_comp_label <- c("Gross operating surplus", "Gross wages", "Employers social contributions", "Net taxes on the production")

data_plot <-  contrib(data_full,"VA", contrib_comp, scenar = c("baseline",scenario_name))

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
              startyear = startyear, endyear = endyear, titleplot = "Contributions to change in value-added (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Value-added and its components

```{r Prod_VA, fig.height = 6, fig.width=14}

contrib_comp <- c("Y", "CI")
contrib_comp_label <- c("Production", "Intermediary consumption")

A <- simpleplot(data_full,c(contrib_comp, c("VA")), c(contrib_comp_label,c("Value-added")), startyear, endyear, titleplot = "Value-added and its components (in difference from baseline)")

data_plot <-  contrib(data_full,"VA", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "CI")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to changes in Value-Added (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Employment

```{r Employment, fig.height = 6, fig.width=14}

A <- simpleplot(data_full,"F_L", label_series = "Labor", startyear, endyear, decimal = 1, titleplot = "Employment (in difference from baseline)")
B <- simpleplot(data_full,"F_L", label_series = "Labor", startyear, endyear, "diff", unit = 1000, decimal = 1, titleplot = "Employment (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Unemployment

```{r Unemployment, fig.height = 6, fig.width=14}

C <- simpleplot(data_full,"UNR", label_series = "Unemployment", startyear, endyear,"diff", unit = 100, titleplot = "Unemployment rate (in difference from baseline)")
D <- simpleplot(data_full,"UNR", label_series = "Unemployment rate (dashed line = baseline)", startyear, endyear, "level", titleplot = "Unemployment rate  (level)")

ggarrange(C,D,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

# Government


## Debt of the Government

```{r Gov_Debt, fig.height = 6, fig.width=14}

variable_macro <- c("RDEBT_G_VAL") %>% toupper()
label_macro <- c("Debt")

A <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"diff", unit = 100, titleplot = "Debt to GDP ratio (in difference from baseline)")

B <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"level", unit = 100, titleplot = "Debt to GDP ratio (dashed line = baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Savings/deficit of the Government

```{r Gov_Savings_deficit, fig.height = 6, fig.width=14}

variable_macro <- c("RSAV_G_VAL", "RBal_G_Prim_VAL", "RBal_G_Tot_VAL") %>% toupper()
label_macro <- c("Savings", "Primary balance", "Total balance")

A <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"diff", unit = 100, titleplot = "Saving to GDP ratio indicators (in difference from baseline)")

B <- simpleplot(data_full, variable_macro, label_macro, startyear, endyear,"level", unit = 100, titleplot = "Saving to GDP ratio indicators  (dashed line = baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

The **Savings of the Government** corresponds to the net lending/borrowing (Income minus spending), which is the published deficit/savings of the Government.

The **Total balance of the Government** corresponds to the savings excluding the reimbursement of the debt from the Government spending. 

The **Primary balance of the Government** corresponds to the savings excluding the reimbursement and the interest paid on the debt from the Government spending. 


## Incomes and spending of the Government

```{r Gov_Savings_Inc_spend, fig.height = 6, fig.width=14}

A <- simpleplot(data_full, c("INC_G_VAL", "SPEND_G_VAL"), label_series =  c("Incomes", "Spending"), startyear, endyear, transformation = "reldiff", titleplot = "Incomes and spending  (in difference from baseline)")

A 

# contrib_comp <- c( "INC_G_VAL", "SPEND_G_VAL")
# contrib_comp_label <- c("Incomes", "Spending")
# 
# data_plot <-  contrib(data_full,"SAV_G_VAL", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff", neg.value = "SPEND_G_VAL")
# 
# B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
#              startyear = startyear, titleplot = "Contributions to change in Saving (in difference from baseline)", line_tot = TRUE)
# 
# 
# ggarrange(A,B,
# labels = c("(a)", "(b)"),
# hjust = -0.5, vjust = 1.5,
# ncol = 2, nrow = 1,
# widths = 2,  heights = 1)


```

## Carbon tax incomes (as a percentage of GDP)

```{r Gov_Carbon Tax, fig.height=6, fig.width=14}

variables_selection = c("T2VAL_SEC","T2VAL_CH", "GDP")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          R_T2VAL_SEC_GDP = T2VAL_SEC / GDP,
          R_T2VAL_CH_GDP = T2VAL_CH / GDP,
          R_T2VAL_GDP = (T2VAL_SEC + T2VAL_CH) / GDP
          )

      ) %>% 
  long_data()

contrib_comp <- c( "R_T2VAL_SEC_GDP", "R_T2VAL_CH_GDP")
contrib_comp_label <- c("Sectors", "Households")

A <- simpleplot(new_indicators, series = contrib_comp, label_series = contrib_comp_label, startyear, endyear, "level", titleplot = "Carbon tax incomes per agent (dashed line = baseline)")


if (new_indicators$baseline[which(new_indicators$year == startyear & new_indicators$variable=="R_T2VAL_GDP")]==0) {
B <- simpleplot(new_indicators, series = "R_T2VAL_GDP", label_series = contrib_comp_label, startyear, endyear, "level", titleplot = "Total carbon tax incomes (dashed line = baseline)")

} else {
  data_plot <-  contrib(new_indicators,"R_T2VAL_GDP", contrib_comp, scenar = c("baseline",scenario_name), indicator = "rel.diff")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
              startyear = startyear, titleplot = "Contributions to the change in Carbon tax incomes (in difference from baseline)", line_tot = TRUE)

}


ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

```

## Prices and wages 

```{r Graph Prices, fig.height = 6, fig.width=14}
label_prices <- c("Consumption", "Production", "Value added","Imports", "Exports")
A <- simpleplot(data_full,c("PCH", "PY", "PVA", "PM", "PX"),label_prices, startyear, endyear, titleplot = "Prices (in difference from baseline)")
B <- simpleplot(data_full,"W", label_series = "wage", startyear, endyear, titleplot = "Gross nominal wages (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust =-0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

# Results per sector (activity)

## Prices of production and of value-added per sector

```{r Exit Knit2: rest of the markdown ignored}
knit_exit()
```

```{r Price_Sect, fig.height = 6, fig.width=14}

variables_selection <-   c(  variables_like(data_com_sec,"^VA_S0",FALSE),
                             variables_like(data_com_sec,"^VA_VAL_S0",FALSE),   
                             variables_like(data_com_sec,"^PY_S0",FALSE),   
                             "PVA", "PY")

calcul_indic <- function(data){
   res <- data

   nb_sect = length(names_sectors$code[which(grepl("^S",names_sectors$code))])

for (i in c(1:nb_sect)){

           res <- mutate(res,
                !!paste0("PVA_S00",i) := get(paste0("VA_S00",i))/get(paste0("VA_VAL_S00",i))   ) 

}

  return(res)
  
}


new_indicators <- data_com_sec %>%  dplyr::filter(variable %in% variables_selection) %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~calcul_indic(.x)) %>% 
  long_data()

A <- curve_sc_plot(new_indicators,"PY", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Production price (in difference from baseline)")

B <- curve_sc_plot(new_indicators,"PVA", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Value- added price (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)


```

## Production per sector

```{r Prod_Sect, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"Y", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Production of sectors (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "Y",
                          group_type = "sector", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total production and sectorial contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Value-Added per sector

```{r VA_Sect, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"VA", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Value-added of sectors (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "VA",
group_type = "sector", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total value-added and sectorial contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Employment per sector

```{r employment_Sect, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"F_L", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Employment of sectors (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "F_L",
group_type = "sector", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total employment and sectorial contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Investment per sector

```{r INV_Sect, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"I", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Investment of sectors (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "I",
group_type = "sector", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total Investment and sectorial contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

# Results per product (commodity)

## Investment per product

```{r INV_Com, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"I", startyear = startyear, endyear = endyear, group_type = "C", growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Investment in commodities (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "I",
group_type = "C", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total investment and commodity contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Intermediary consumption per product

```{r CI_Com, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"CI", startyear = startyear, endyear = endyear, group_type = "C", growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Intermediary consumption in commodities (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "CI",
group_type = "C", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total intermediary consumption and commodity contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## Households' final consumption per product

```{r CH_Com, fig.height = 6, fig.width=14}

A <- curve_sc_plot(data_com_sec,"CH", startyear = startyear, endyear = endyear, group_type = "C", growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Households' consumption in commodities (in difference from baseline)")

data_plot <- contrib.sub(data_com_sec,var1 =  "CH",
group_type = "C", scenar = c("baseline", scenario_name))

B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Total Households' consumption and commodity contribution (in difference from baseline)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```


## Commodity prices

```{r PCH_com Wage Sect, fig.height = 6, fig.width=14}


A <- curve_sc_plot(data_com_sec,"PCH", group_type = "C", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Household's Consumption price per commodity (in difference from baseline)")



B <- curve_sc_plot(data_com_sec,"PCI", group_type = "C", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Intermediary consumption price per commodity (in difference from baseline)")


ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)


```

## Consumption prices for imported and domesticly producted commodities

```{r PCH_DM_com Wage Sect, fig.height = 6, fig.width=14}


A <- curve_sc_plot(data_com_sec,"PCHD", group_type = "C", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Domesticly producted commodities (in difference from baseline)")



B <- curve_sc_plot(data_com_sec,"PCHM", group_type = "C", startyear = startyear, endyear = endyear, growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Imported commodities (in difference from baseline)")


ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)


```

# GHG emissions

## GHG emissions per driver

```{r GHG emissions, fig.height = 6, fig.width=14}

variables_selection = c("EMS_CI", "EMS_Y", "EMS_MAT", "EMS_CH", "EMS")

new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          EMS_PROD = EMS_MAT  + EMS_Y)
      
      ) %>% 
  long_data()

contrib_comp <- c("EMS_CI", "EMS_PROD", "EMS_CH")
contrib_comp_label <- c("Intermediary consumption", "Production process", "Household's final consumption")

A <- simpleplot(new_indicators,c(contrib_comp, c("EMS")), c(contrib_comp_label,c("Total GHG emssions")), startyear, endyear, titleplot = "GHG emissions and its components (in difference from baseline)")

data_plot <-  contrib(new_indicators, "EMS", contrib_comp, scenar = c("baseline",scenario_name))

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to changes in GHG emissions (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

## GHG emissions per source

```{r GHG emissions per source, fig.height=6, fig.width=14}

variables_selection <-   c(  variables_like(data_com_sec,"^EMS_CI_C0",FALSE),
                             variables_like(data_com_sec,"^EMS_CH_C0",FALSE),   
                             "EMS_CI", "EMS_CH"  )

calcul_indic <- function(data){
   res <- data
   res <- mutate(res,     
          EMS_CI_CH = EMS_CI + EMS_CH)

   
nb_com = length(names_commodities$code[which(grepl("^C",names_commodities$code))])

 for (i in c(1:nb_com)){

   if(exists(paste0("EMS_CI_C00",i), data ) & exists(paste0("EMS_CH_C00",i), data )  ){   
     res <- mutate(res,
                !!paste0("EMS_CI_CH_C00",i) := get(paste0("EMS_CI_C00",i)) + get(paste0("EMS_CH_C00",i)) ) 
   }

   if(exists(paste0("EMS_CI_C00",i), data ) & !exists(paste0("EMS_CH_C00",i), data )  ){   
     res <- mutate(res,
                !!paste0("EMS_CI_CH_C00",i) := get(paste0("EMS_CI_C00",i))  ) 
   }
   
   
   if(!exists(paste0("EMS_CI_C00",i), data ) & exists(paste0("EMS_CH_C00",i), data )  ){   
     res <- mutate(res,
                !!paste0("EMS_CI_CH_C00",i) :=  get(paste0("EMS_CH_C00",i)) ) 
   }

 }

    return(res)
  
}

new_indicators <- data_com_sec %>%  dplyr::filter(variable %in% variables_selection) %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~calcul_indic(.x)) %>% 
  long_data()

A <- curve_sc_plot(new_indicators,"EMS_CI_CH", startyear = startyear, endyear = endyear, group_type = "C", growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "GHG emissions per source (in difference from baseline)")

# BUG to calculate contrib when defined for only one commodity: write in issue
# data_plot <- contrib.sub(new_indicators,var1 =  "EMS_CI_CH",
# group_type = "C", scenar = c("baseline", scenario_name))
# 
# B <- contrib.sub.plot(data_plot, template = "ofce", startyear = startyear, endyear = endyear, line_tot =  TRUE, titleplot = "Contributions to changes in GHG emissions (in difference from baseline)")

B <- A

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```

