---
title: "Impact of an increase in oil and gas price"
subtitle: "Scenario: `r params$scenario_name`"
author: "ThreeME team"
date: "`r format(Sys.Date(), '%d %B %y')`"
output:
  html_document:
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    df_print: paged
    code_folding: show
  word_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
params:
  startyear: 2020
  endyear: 2050
  scenario_name: oilprice_fra
  classification: c28_s32
  template_default: classic
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
```

```{r Plots default options}



startyear <- params$startyear
endyear <- params$endyear
scenario_name <- params$scenario_name
classification <- params$classification
template_default <- params$template_default

```




To plot ThreeME results several package are required:

```{r Required packages, message=FALSE, warning=FALSE}

source("src/functions.R")
data_full<-readRDS(file = paste0("databases/",scenario_name,"_",classification,".rds"))

```


# Macroeconomic results


## Impact on GDP and employment


This scenario leads to the following macroeconomic results.


```{r Graph GDP, fig.height=6.3, fig.width=12.6}
label_macro <- c("Gross domestic Production", "Households consumption", "Investment", "Public spendings")
A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, titleplot = "GDP and its components")

B <- simpleplot(data_full,c("X", "M"),label_series = c("Exports", "Imports"), startyear, endyear, titleplot = "External trade")

C <- simpleplot(data_full,"UNR", label_series = "Unemployment", startyear, endyear,"diff", titleplot = "Unemployment rate")
D <- simpleplot(data_full,"F_L", label_series = "Labor", startyear, endyear, "diff", unit = 1000, decimal = 1, titleplot = "Employment")

macro <- ggarrange(A,B,C,D,
                   labels = c("(a)", "(b)", "(c)", "(d)"),
                   hjust = -0.5, vjust = 1.5,
                   ncol = 2, nrow = 2,
                   widths = 2,  heights = 1)

 ## Save image on disk for further use (ready to be activated)
 # ggsave("macro.svg", device = svg, width = 32,  height = 16, units = c("cm"))


  ## See the graph in Mark-down
  macro



```

[comment]: <> (If the plot is saved with ggsave by activating line in chunk above, the line below add gthe graph with a title)

[comment]: <> (<div align="center">![<span style="font-family:mono; font-size:2em;">**Main macroeconomic indicators** </span>](macro.svg))


## Other Results

```{r other Graphs, fig.height=6.3, fig.width=12.6}

A <- simpleplot(data_full,c("RBAL_TRADE_VAL", "RBAL_G_PRIM_VAL"), label_series = c("Trade Balance", "Public Primary Balance"), startyear, endyear, "diff", titleplot = "Public and Trade Balance (in point of GDP)")

B <- simpleplot(data_full,c("RDEBT_G_VAL"),label_series = "Public Debt", startyear, endyear, "diff", titleplot = "Public Account (in point of GDP)")

C <- simpleplot(data_full,"W", label_series = "wage", startyear, endyear, titleplot = "Gross nominal wage")
D <- simpleplot(data_full,"EMS_CO2", label_series = "Emissions", startyear, endyear, titleplot = "CO2 Emissions")

macro_others <- ggarrange(A,B,C,D,
                   labels = c("(a)", "(b)", "(c)", "(d)"),
                   hjust = -0.5, vjust = 1.5,
                   ncol = 2, nrow = 2,
                   widths = 2,  heights = 1)

 ## Save image on disk for further use (ready to be activated)
 # ggsave("macro.svg", device = svg, width = 32,  height = 16, units = c("cm"))


  ## See the graph in Mark-down
  macro_others
  

  
E <- simpleplot(data_full,"EMS_CO2", label_series = "Emissions", startyear, endyear, transformation = "level", unit =  1, decimal = 1, titleplot = "CO2 Emissions")
E  

```


## GDP and its contributions

Decomposing the effect of the GDP by contribution of its elements leads to the following results
```{r contrib Graphs, fig.height=6.3, fig.width=12.6}
GDP_comp <- c( "CH","X","M", "I", "G","DS")
GDP_comp_label <- c( "Households consumption","Exports","Imports", "Investment", "Public administration","Stock variation")

data_plot <-  contrib(data_full,"GDP", GDP_comp, scenar = c("baseline",scenario_name))



A <- contrib.plot(data_plot, series = GDP_comp, 
             label_series = GDP_comp_label,
                      startyear = 2020)
A
```

## Impact on prices
```{r Graph Prices}
label_prices <- c("Consumption price", "Production price", "Value added price","Imports price", "Exports price")
A <- simpleplot(data_full,c("PCH", "PY", "PVA", "PM", "PX"),label_prices, startyear, endyear)
A
```

## Baseline versus scenario


```{r Graph Macro Growth rate, fig.height=6.3, fig.width=12.6}
A <- simpleplot(data_full,c("GDP", "CH", "I", "G"), label_macro, startyear, endyear, "gr", titleplot = "GDP and its components")

B <- simpleplot(data_full,c("X", "M"), c("Exports", "Imports"), startyear, endyear, "gr", titleplot = "External trade")

C <- simpleplot(data_full,"UNR","Unemployment rate", startyear, endyear, "level", titleplot = "Unemployment rate")
D <- simpleplot(data_full,"F_L","Labor", startyear, endyear, "gr", titleplot = "Employment")


  macro_gr <- ggarrange(A,B,C,D,
            labels = c("(a)", "(b)", "(c)", "(d)"),
            hjust = -0.5, vjust = 1.5,
            ncol = 2, nrow = 2,
            widths = 2,  heights = 1)

  # Activate to save the graph
  #  ggsave("macro_gr.svg", device = svg, width = 32,  height = 16, units = c("cm"))

  ## Activate to see the result from the script
  macro_gr

```

# Sectoral results
```{r Sector or  Commodity agregation, eval=TRUE, include=FALSE}
### loading the sector and commodity aggregated database 
data_sector <- readRDS(file = paste0("databases/",scenario_name,"_",classification,"_commodities_sectors.rds"))


```

```{r barplots for sectors}
## compute CO2 emission per sector
data_CO2 <- data_sector %>% filter(year %in% (startyear:endyear)) %>% filter(grepl("^EMS_.+_CO2_S.*$",variable)) %>% 
  mutate(variable = str_remove(variable,"_(CI|MAT|Y)")) %>% 
  group_by(year,sector,variable) %>% 
  summarise_at(all_of(c("baseline",scenario_name)), sum) %>% ungroup()

stacked_sc_plot(data_CO2,"EMS_CO2",interval = 5, diff = TRUE, title = "Emissions de CO2 par secteur, en écart au baseline")
stacked_sc_plot(data_CO2,"EMS_CO2",scenario = c("baseline",scenario_name),interval = 10, title = "Emissions de CO2 par secteur")
curve_sc_plot(data_CO2,"EMS_CO2", growth.rate = TRUE,diff = TRUE,abs.diff = TRUE, title = " Croissance des émissions de CO2 par secteur, en point d'écart au baseline")

```

## Output

```{r output graphs}
curve_sc_plot(data_sector,"Y", growth.rate = TRUE,scenario = c("baseline",scenario_name), title = "Evolution de la production par secteur")

curve_sc_plot(data_sector,"Y", growth.rate = TRUE,diff = TRUE,abs.diff = TRUE, title = "Evolution de la production par secteur, en point d'écart au baseline")

curve_sc_plot(data_sector,"Y", growth.rate = FALSE,diff = TRUE,abs.diff = FALSE, title = "Production par secteur, en % d'écart au baseline")

curve_sc_plot(data_sector,"Y", growth.rate = FALSE,diff = FALSE,abs.diff = FALSE, title = "Production par secteur")
```

## Employment
```{r employement plots}
curve_sc_plot(data_sector,"F_L",diff=TRUE,abs.diff = TRUE,title = " Evolution des effectifs employés en fonction des secteurs (en écart au baseline)")

curve_sc_plot(data_sector,"F_L",title = " Evolution des effectifs employés en fonction des secteurs")
```

## Value added

```{VA plots}
curve_sc_plot(data_sector,"VA",diff=FALSE,growth.rate = TRUE,title = " Croissance de la VA par secteur")
curve_sc_plot(data_sector,"VA",diff=TRUE,growth.rate = TRUE,abs.diff = TRUE,title = " Croissance de la VA par secteur (en point de différence par rapport au baseline)")
```

## Contribution to aggregate deviation 
```{Contrib.sub plots}
compute Y production contribution per sector
data_plot <- contrib.sub(data_full,var1 =  "Y",
                        group_type = "sector", scenar = c("baseline", scenario_name))

contrib.sub.plot(data_plot, template = "ofce", startyear = 2020, endyear = 2050, line_tot =  TRUE)
```
## Impact on oil 
```{r}

```

