---
title: "Test yourself: Simulation and graphs"
subtitle: "Scénario: `r params$scenario_name`"
author: "ThreeME team"
date: "`r format(Sys.Date(), '%d %B %y')`"
output:
  slidy_presentation: 
    theme: sandstone
    highlight: monochrome
    toc: true
    number_sections: true
    toc_depth: 3
params:
  startyear: 2020
  endyear: 2035
  scenario_name: g_tra
  classification: c0_s0
  compil: compil
  Rsolver: Rsolver
  githubrepo: ThreeME-R-training
  template_default: ofce
---

```{r setup, include=FALSE}

work.dir <- stringr::str_remove(getwd(),"/results/report/markdown/training")
knitr::opts_knit$set(root.dir = work.dir)

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
```

```{r Plots default options}

startyear <- params$startyear
endyear <- params$endyear
scenario_name <- params$scenario_name
classification <- params$classification
template_default <- params$template_default

```


```{r Required packages, message=FALSE, warning=FALSE}

# Load functions
source("src/functions.R")


```


```{r load data and bridges}

data_full<-readRDS(file = paste0("data/output/",scenario_name,"_",classification,".rds"))

view(data_full)

```


# Exercice

## Preliminary Instructions
- Work on your **own branch** you created from the branch "Session01"
- Write down your answers starting from this Markdown file 
- Build your model in a new equation file that you will create as a copy of the **"01.1-eq.mdl"** file (the new equation file should be in the same location as the initial "01.1-eq.mdl" file)
- In this exercice, we consider the following calibration file: **"01.1-calib.mdl"** (don't change this file for questions 1 to 7)

## Questions (10 pts)

We consider a simple model where :

- Production equals demand. 
- Households Consumption is defined as a fixed share of past production **(consumption share = 0.6)**. 
- Investment is determined as fixed share of production **(investment share = 0.25)**.

1. Which equations are missing? Complete your equation file with all needed equations. Run the main.(1pt)
2. List all endogenous and exogenous variables in the model. (1pt)

<span style="color: grey;">*For questions 3 to 7, you can have a look on the markdown "Training_01_FirstSteps.Rmd" if needed*.</span>


3. Plot variables Y, CH and I in level from 2020 to 2030 (in two-year time step) . Give a name to your plot. (1pt)
4. We introduce a shock on G of 2 GDP points starting from 2022. Show two differents ways to write this shock (in chunks). (2pts)
5. Plot variables Y, G, CH and I in relative difference from the baseline (Graph A). (2pts)
6. Plot variables Y, G, CH and I in difference (Graph B). (2pts)
7. Put Graph A and Graph B one next to the other. (1pt)

 
<span style="color: brown;">**Bonus**</span>

We consider now that the consumption share is **0.5** and the investment share is **0.2**. Adapt consequently the calibration file.   


# Answers
```{r}
view(data_full)
```

```{r Table data_full endyear, include=FALSE, results='asis'}
variables_selection = c("Y","CH","I", "G")
selection <-  data_full %>% filter(variable %in% variables_selection, year %in% c(endyear)) %>% select(-sector, -commodity, -year) %>% arrange(variable)
flextable(selection)
```


1. There are two missing equations:   
- **Households consumption equation**:     
\begin{equation}
CH = 0.6* Y_{t-1}
\end{equation}
- **Investment equation**:   
\begin{equation}
I = 0.25* Y
\end{equation}

2. Endogenous variables : **Y, CH** and **I** and Exogenous variables : **G**     

3. Plot CH, I and Y in level       
```{r plot1}
plot1 <- simpleplot(data_full,c("CH", "I", "Y"), startyear = 2020, endyear= 2030,  transformation = "level", titleplot = "Production, Investment and Households consumption in level",custom_x_breaks = 2,
                decimal = 0.1, unit = 1 )
plot1
```

4. Shock of 2 GDP points starting from 2022          
```{r echo=TRUE, eval=FALSE}
shock_ch <- mutate(selection,
                    g =   ifelse(year >= 2022, g + 2, g)
                   )
```
Or    
```{r echo=TRUE, eval=FALSE}
shock_ch <- mutate(selection,
                    g =   ifelse(year >= 2022, g + 0.02*y[which(year == baseyear)], g)
                  )
```

5. Plot Y, CH, I annd G in relative difference (A)        
```{r}
A <- simpleplot(data_full,c("CH", "I", "Y", "G"), startyear = 2020, endyear= 2030,  transformation = "reldiff", titleplot = "GDP and its components in relative difference (A)",custom_x_breaks = 2,
                decimal = 0.1, unit = "percent" )
A
```
 
6. Plot Y, G, CH and I in difference (B)        
```{r}
B <- simpleplot(data_full,c("CH", "I", "Y", "G"), startyear = 2020, endyear= 2030,  transformation = "diff", titleplot = "GDP and its components in relative difference (B)",custom_x_breaks = 2,
                decimal = 0.1, unit = 1 )
B
```

7. PLot A et B together       
```{r}
A <- simpleplot(data_full,c("CH", "I", "Y", "G"), startyear = 2020, endyear= 2030,  transformation = "reldiff", titleplot = "GDP and its components 
in relative difference (A)",custom_x_breaks = 2,
                decimal = 0.1, unit = "percent" ) + theme(text = element_text(size = 10))

B <- simpleplot(data_full,c("CH", "I", "Y", "G"), startyear = 2020, endyear= 2030,  transformation = "diff", titleplot =  "   GDP and its components 
in difference (B)",custom_x_breaks = 2,
                decimal = 0.1, unit = 1 ) + theme(text = element_text(size = 10))
C <- ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 2)
C

```

**Bonus**
The new equations are:
- **Households consumption equation**:     
\begin{equation}
CH = 0.5* Y_{t-1}
\end{equation}
- **Investment equation**:   
\begin{equation}
I = 0.2* Y
\end{equation}
