---
title: "Modules 3: a small neo-keynesian model - Open Economy"
subtitle: "Scenario: `r params$scenario_to_analyse`"
author: "ThreeME team"
date: "`r format(Sys.Date(), '%d %B %y')`"
output: 
  revealjs:
    theme: sandstone
   # highlight: monochrome
  #  toc: true
   # number_sections: true
    #toc_depth: 3
params:
  startyear: 2020
  endyear: 2035
  project_name: "multi_shock"
  project_title: "Simulation with small general equilibrium model"
  scenario_to_analyse: g
  classification: c0_s0
  compil: compil
  Rsolver: Rsolver
  githubrepo: ThreeME-R-training
  template_default: ofce

---

```{r setup, include=FALSE}

work.dir <- stringr::str_remove(getwd(),"/results/report/markdown/training")
knitr::opts_knit$set(root.dir = work.dir)

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
```

```{r Plots default options}

startyear <- params$startyear
endyear <- params$endyear
scenario_to_analyse <- params$scenario_to_analyse
project_name <- params$project_name
classification <- params$classification
template_default <- params$template_default
githubrepo <- params$githubrepo

## SHOULD BE DELETED WHEN OPTION DE SIMPLEPLOT ERMEETH CHANGES:
# scenario = scenario_to_analyse (and not scenario_name)
scenario_name <- scenario_to_analyse

```


```{r Required packages, message=FALSE, warning=FALSE}

# Load functions
source("src/functions.R")


```


```{r load data and bridges}

data_full<-readRDS(file = file.path("data","output", paste0(project_name,".rds")))


```

# Changes compared to close economy


## New equations for open economy

- **Production**

\begin{equation}
Y + M = CH + I + G + X
\end{equation}

- **Average user price**

\begin{equation}
p . \left( Y + M \right) = py . Y + pm . M
\end{equation}

- **Notional production price **

\begin{equation}
py^{n} . Y = c^{Y} . Y . \left( 1 + m^{up} + dm^{up} \right)
\end{equation}

- **International trade**


**Imports**

\begin{equation}
M = \left( Y + M \right) . \varphi^{M} . \left( \frac{pm}{p} \right) ^ {\left( -\rho^{M} \right)}
\end{equation}

**Exports**

\begin{equation}
X = WD . \left( \frac{py}{pw} \right) ^ {\left( -\rho^{X} \right)}
\end{equation}

**Saving of the Rest of the World**

\begin{equation}
SAV^{ROW} = pm . M - py . X
\end{equation}



# Macroeconomic results (Open economy)

## Considered shocks

- Shock of 1% GDP point on G (public spending)      
- Shock of 1% GDP point on wd (world demand)                    
      

## Contributions to GDP (Import and Export separately)

```{r contrib in GDP opened economy with X and M, echo=FALSE, fig.height=6, fig.width=14}

contrib_comp <- c( "CH", "I", "G", "X", "M")
contrib_comp_label <- c("Households consumption", "Investment", "Public spending", "Exports", "Imports")

data_plot <-  contrib(data_full,"Y", contrib_comp, scenar = c("baseline",scenario_to_analyse), neg.value = "M")

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = " Contributions to change in GDP (in relative difference from baseline)", line_tot = TRUE)  


B <- simpleplot(data_full, c("X", "M"), c("Exports", "Imports"), startyear, endyear, "gr", titleplot = "External trade (in growth rates)")

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)


```


## Contributions to GDP (with trade balance)

```{r contrib GDP with trade balance, echo=FALSE, fig.height=6, fig.width=14}

variables_selection = c("Y","X", "M", "I", "CH","G")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          BAL_TRADE = X - M)) %>% long_data(sector_names_table=NULL,commodity_names_table=NULL) %>% select(-sector,-commodity)

contrib_comp <- c( "I", "CH", "G", "BAL_TRADE")
contrib_comp_label <- c( "Investment", "Households consumption", "Public spending", "Trade balance")

data_plot <-  contrib(new_indicators,"Y", contrib_comp, scenar = c("baseline",scenario_to_analyse))

A <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in GDP (in difference from baseline)", line_tot = TRUE)

contrib_comp <- c( "X", "M")
contrib_comp_label <- c("Exports", "Imports")

data_plot <-  contrib(new_indicators,"BAL_TRADE", contrib_comp, scenar = c("baseline",scenario_to_analyse), indicator = "rel.diff", neg.value = "M")

B <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, endyear = endyear, titleplot = "Contributions to change in trade balance (in difference from baseline)", line_tot = TRUE)

ggarrange(A,B,
          labels = c("(a)", "(b)"),
          hjust = -0.5, vjust = 1.5,
          ncol = 2, nrow = 1,
          widths = 2,  heights = 1)

```



## GDP and its components 

```{r Graph contrib, echo=FALSE, fig.height=6, fig.width=14}

variable_macro <- c( "Y", "CH", "I", "G", "M", "X")
label_macro <- c("GDP", "Households consumption", "Investment", "Public spending", "Imports", "Exports")

A <- simpleplot(data_full,variable_macro, label_macro, startyear, endyear,  transformation = "reldiff", titleplot = " GDP and its components (in relative difference from baseline)",
           unit = "percent", decimal = 0.1 )

B <- simpleplot(data_full,variable_macro, label_macro, startyear, endyear,  transformation = "gr", titleplot =  " GDP and its components (in growth rate)")

macro <- ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

## Save image on disk for further use (ready to be activated)
# ggsave("macro.svg", device = svg, width = 32,  height = 16, units = c("cm"))

## See the graph in Mark-down
macro

```


## Ratio between exports and imports

```{r creation ratio  export to import, echo=FALSE, fig.height=6, fig.width=14}

variables_selection = c("X","M")
new_indicators <- data_full %>% wide_data(variables = variables_selection,out_format = "list") %>%
  map(~.x %>% mutate(RATIO_X_M= X/M)) %>% long_data(sector_names_table=NULL,commodity_names_table=NULL) %>% select(-sector,-commodity)

A <- simpleplot(new_indicators, c("RATIO_X_M"), c("X/M"), startyear, endyear, "reldiff", titleplot = " Ratio  exports to imports(in relative difference from baseline)")

B <- simpleplot(new_indicators, c("RATIO_X_M"), c("X/M"), startyear, endyear, "level", titleplot = " Ratio exports to imports(in relative difference from baseline)", unit = 1, decimal = 0.01) 

macro <- ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

macro
```

## Production, capital and investment 

```{r Graph K and I, fig.height=6, fig.width=14}

variable_macro <- c( "K","K_N","I")
label_macro <- c("Capital",  "Notional Capital", "Investment")

A <- simpleplot(data_full,variable_macro, label_macro, startyear, endyear,  transformation = "reldiff", titleplot = " GDP, Capital and Investment (in relative difference from baseline) " )

B <- simpleplot(data_full,variable_macro, label_macro, startyear, endyear,  transformation = "gr", titleplot = " GDP, Capital and Investment (in growth rate)",
           unit = "percent", decimal = 0.1 )

macro <- ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

## Save image on disk for further use (ready to be activated)
# ggsave("macro.svg", device = svg, width = 32,  height = 16, units = c("cm"))

## See the graph in Mark-down
macro

```

## Labor and Unemployment 

```{r Graph L and U, fig.height=6, fig.width=14}

variable_macro <- c( "L","L_N")
label_macro <- c("Labor",  "Notional labor")

A <- simpleplot(data_full,variable_macro, label_macro, startyear, endyear,  transformation = "reldiff", titleplot = " Effective and notional labor (in relative difference from baseline)" )

B <- simpleplot(data_full,"U", "Unemployment rate", startyear, endyear,  transformation = "level", titleplot = " Unemployment rate (in level)",
           unit = "percent", decimal = 0.1 )

macro <- ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

## Save image on disk for further use (ready to be activated)
# ggsave("macro.svg", device = svg, width = 32,  height = 16, units = c("cm"))

## See the graph in Mark-down
macro

```


## Prices and wages 

```{r Graph Prices, fig.height=6, fig.width=14}

A <- simpleplot(data_full,c("P", "W"), c("Price", "Wages"), startyear, endyear, "reldiff", titleplot = " Prices and wages (in relative difference from baseline)")

B <- simpleplot(data_full,c("P", "W"), c("Price", "Wages"), startyear, endyear,  transformation = "gr", decimal= 0.1, unit="percent",  titleplot =  "  Prices and wages (in growth rates)" )

ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

```

## Mark-up

```{r Mark-up,fig.height=6, fig.width=14 }
A <- simpleplot(data_full,c("M_UP"), c("Mark-up"), startyear, endyear, "level", titleplot = " Mark-up (in level)")

B <- simpleplot(data_full,c("M_UP"), c("Mark-up"), startyear, endyear, "diff", unit = "percent", decimal = 0.1,  titleplot = " Mark-up (in difference from baseline)")

ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)
```


## Interest rate

```{r Graph Interest rate, fig.height=6, fig.width=14}

A <- simpleplot(data_full,c("R"), c("Interest rate"), startyear, endyear, "level", titleplot = " Interest rate (Level) ")

B <- simpleplot(data_full,c("R"), c("Interest rate"), startyear, endyear, "diff", titleplot = " Interest rate (in difference from baseline)")

ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)

```


## Propensity to save

```{r Propensity to save , fig.height=6, fig.width=14}
A <- simpleplot(data_full,c("SIGMA"), c("Propensity to save"), startyear, endyear, "level", unit = "percent", decimal = 0.1,  titleplot = " Propensity to save (in level)")

B <- simpleplot(data_full,c("SIGMA"), c("Propensity to save"), startyear, endyear, "diff", titleplot = " Propensity to save (in difference from baseline)")

ggarrange(A,B,
labels = c("(a)", "(b)"),
hjust = -0.5, vjust = 1.5,
ncol = 2, nrow = 1,
widths = 2,  heights = 1)
```


## Debt to GDP ratio

```{r creation variable debt to gdp, fig.height=6, fig.width=14}
variables_selection <- c("Y", "DEBT_G", "P")
new_indicators <- data_full%>%
wide_data(variables = variables_selection, out_format = "list")%>%
map(~.x %>% mutate (Ratio_debt_gdp = DEBT_G/(P*Y)))%>%
long_data(sector_names_table = NULL, commodity_names_table = NULL)%>%
select(-sector,-commodity)

A <- simpleplot (new_indicators, c("Ratio_debt_gdp"), c("DEBT_G/(P*Y)"), startyear, endyear,"level", unit = "percent", decimal = 0.1, titleplot = "Debt to GDP ratio (in level)")


B <- simpleplot(new_indicators, c("Ratio_debt_gdp"), c("DEBT_G/(P*Y)"), startyear, endyear, "diff", titleplot = "Debt to GDP ratio (in difference from baseline)")

macro <- ggarrange(A, B,
labels= c("(a)", "(b)"), 
hjust = -0.5, vjust = 1.5,
ncol= 2, nrow=1, 
widths =2 , heights = 2)

macro

```


## Mains impacts of a shock on G

- **The third model (Open economy):**

  - Same effects in a close economy with an increase of exports contribution to GDP
  - Positive effect on GDP on the long run
  




```{r Exit Knit: rest of the markdown ignored}
knit_exit()
```



# PLots "Neo-Keynesian" closure open (overleaf)


## Contribution to GDP open economy (overleaf)

```{r contrib GDP with trade balance open ovr,  fig.height=6, fig.width=14}

variables_selection = c("Y","X", "M", "I", "CH","G")
new_indicators <- data_full %>% 
  # 1. Put in Wide format
  wide_data(variables = variables_selection , out_format = "list") %>%  ## 1. passe en wide
  # 2. Calculate indicators
  map(~.x %>%          
        mutate(
          BAL_TRADE = X - M)) %>% long_data(sector_names_table=NULL,commodity_names_table=NULL) %>% select(-sector,-commodity)

contrib_comp <- c( "I", "CH", "G", "BAL_TRADE")
contrib_comp_label <- c( "Investment", "Households consumption", "Public spending", "Trade balance")

data_plot <-  contrib(new_indicators,"Y", contrib_comp, scenar = c("baseline",scenario_to_analyse))

Contrib_GDP_NeoKey_op <- contrib.plot(data_plot, series = contrib_comp,label_series = contrib_comp_label,
             startyear = startyear, line_tot = TRUE, custom_x_breaks = 5) + theme(axis.text.y = element_text(size = 28)) +
theme(axis.text.x = element_text(size = 28)) +
theme(text = element_text(size = 28)) +
theme(legend.text= element_text(size = 28))

## Save image on disk for further use (ready to be activated)
ggsave("Contrib_GDP_NeoKey_op.png",width = 48,  height = 28, units = c("cm"))


## See the graph in Mark-down
Contrib_GDP_NeoKey_op

```